IMF and Benchmark Forecasts

### 2023-09-06 manuscript/manuscript.Rmd
visualize scores and coverage

---
title: "Compare forecats"
header-includes:
    - \usepackage{lineno}
    - \linenumbers
    -  \newcommand{\beginsupplement}{\setcounter{table}{0}  \renewcommand{\thetable}{S\arabic{table}} \setcounter{figure}{0} \renewcommand{\thefigure}{S\arabic{figure}}}
output: 
  bookdown::pdf_document2:
    extra_dependencies: ["float"]
    keep_tex:  true
    toc: false
linestretch: 2 
bibliography:
  - references.bib
csl: vancouver.csl
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

This is an R Markdown document. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document. You can embed an R code chunk like this:

```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.

>>>>

---
title: "IMF and Benchmark Forecasts"
header-includes:
    - \usepackage{lineno}
    - \linenumbers
    -  \newcommand{\beginsupplement}{\setcounter{table}{0}  \renewcommand{\thetable}{S\arabic{table}} \setcounter{figure}{0} \renewcommand{\thefigure}{S\arabic{figure}}}
output: 
  bookdown::pdf_document2:
    extra_dependencies: ["float"]
    keep_tex:  true
    toc: false
linestretch: 2 
bibliography:
  - references.bib
csl: vancouver.csl
---

```{r setup, include=FALSE}
library(data.table)
library(here)
library(ggplot2)
library(patchwork)
library(MetBrewer)
library(purrr)
library(lattice)
library(gt)
library(rlang)
library(tidyverse)
devtools::load_all()
knitr::opts_chunk$set(echo = TRUE)
.d <- `[`
```

# A short note on error handling

In almost all 72 cases, absolute error handling gives lower scores than directional error handling. The only exception is the inflation series for the IMF forecasts and horizon 0, where the expanding window and rolling window method give \textit{slightly} lower scores for the directional methodology. 
We thus decide to focus on the absolute errors in this document.

# Scores, by estimation method, Horizon and forecast source 
```{r, echo = FALSE}
scores <- fread(here("quantile_forecasts", "ci_scores.csv"))

wis_scores <- fread(here("quantile_forecasts", "ci_scores_avgcnt.csv")) |>
  data.table::copy() |>
  .d(, .(model, error_method, method, target, horizon, interval_score, dispersion, underprediction, overprediction)) |>
  setnames("model", "source")

crps_scores <- fread(here("quantile_forecasts", "sample_scores.csv"))

all_scores <- 
  crps_scores[wis_scores, on = c("source", "error_method", "method", "target", "horizon")]|>
  .d(error_method == "absolute") |>
  .d(, error_method := NULL)

gather_scores <- all_scores |>
  data.table::copy() |>
  .d(target == "pcpi_pch") |>
  .d(,target := NULL) |>
  .d(, .(horizon, method, source, score, interval_score)) |>
  setnames("score", "sample_crps") |>
  melt(id.vars = c("horizon", "method", "source"), variable.name = "score_type", value.name = "score") |>
  .d(, combms := paste0(method,"_", score_type)) |>
  .d(, .(horizon, source, combms, score)) |>
  .d(, horizon := paste0("horizon = ", horizon)) |>
  .d(, score := round(score, 3)) |>
  dcast(horizon + combms ~ source, value.var = "score")

gather_scores |>
  data.table::copy() |>
  gt(rowname_col = "combms", groupname_col = "horizon") |>
  cols_label(
      IMF = "IMF",
      ar = "ar",
      bvar = "bvar"
    )

col_names <- c("IMF", "ar", "bvar")

```

## Inflation

```{r, echo = FALSE, warning=FALSE,fig.dim = c(10, 12)}

plots_is <- vector(mode = "list", length = 4)
plots_cr <- vector(mode = "list", length = 4)

for(i in 1:4){

  hor <- (i-1)*0.5

  mydat <- gather_scores |>
    .d(horizon == paste0("horizon = ", hor)) |>
  .d(grep("interval", combms)) |>
  melt(id.vars = c("horizon", "combms"), variable.name = "source", value.name = "score") |>
  .d(, c("method", "scorem", "extra") := tstrsplit(combms, "_", fixed=TRUE))

  plots_is[[i]] <- ggplot(mydat, aes(x = source, y = method)) +
  geom_tile(aes(fill = score)) +
    guides(fill = FALSE) +
    ggtitle(paste0("horizon = ", hor, " - Weighted Interval Score"))
}

for(i in 1:4){

  hor <- (i-1)*0.5

  mydat <- gather_scores |>
    .d(horizon == paste0("horizon = ", hor)) |>
  .d(grep("crps", combms)) |>
  melt(id.vars = c("horizon", "combms"), variable.name = "source", value.name = "score")|>
  .d(, c("method", "scorem", "extra") := tstrsplit(combms, "_", fixed=TRUE))

  plots_cr[[i]] <- ggplot(mydat, aes(x = source, y = method)) +
  geom_tile(aes(fill = score))+
    guides(fill = FALSE)+
    ggtitle(paste0("horizon = ", hor, " - CRPS by sample"))
}

ovr_plot <- 
  (plots_is[[1]] + plots_cr[[1]]) /
  (plots_is[[2]] + plots_cr[[2]]) /
  (plots_is[[3]] + plots_cr[[3]]) /
  (plots_is[[4]] + plots_cr[[4]]) +
  plot_layout(heights = c(1, 1,1,1)) &
    plot_annotation(tag_levels = 'I')  &
    theme(legend.position = 'right', 
          legend.box="vertical", legend.margin=margin())

ovr_plot

```

```{r cvgdat2, include=FALSE, echo = FALSE}

scores <- fread(here("quantile_forecasts", "ci_scores.csv"))
scores_cvgshort <- fread(here("quantile_forecasts", "cvg_pooled.csv"))

cvg_rg <- c(50, 80)

cols <- paste0("coverage_", cvg_rg)

large_cvgdat <- scores |>
  setnames("model", "source") |>
  .d(, c("country", "horizon", "target", "error_method", "method", "source", cols), with = FALSE) |>
  melt(id.vars = c("country", "horizon", "target", "error_method", "method", "source"),
       variable.name = "pilvl",
       value.name = "coverage") |>
  .d(, pilvl := gsub("^.*?coverage_","",pilvl)) |>
  .d(, pilvl := as.numeric(pilvl)/100) |>
  .d(, idcol := paste0(horizon, country, method)) |>
  .d(, country := NULL) |>
  .d(, horizon := NULL)

cvgdat <- scores_cvgshort |>
  setnames("model", "source") |>
  .d(, c( "target", "error_method", "method", "source", cols), with = FALSE) |>
  melt(id.vars = c("target", "error_method", "method", "source"),
       variable.name = "pilvl",
       value.name = "coverage") |>
  .d(, pilvl := gsub("^.*?coverage_","",pilvl)) |>
  .d(, pilvl := as.numeric(pilvl)/100)

cvgdat_cpi <- cvgdat |>
  .d(target == "pcpi_pch")

cvgdat_gdp <- cvgdat |>
  .d(target == "ngdp_rpch")

plot_cpi <- ggplot() +
  geom_line(aes(x = pilvl,
                y = coverage,
                group = idcol),
            data = large_cvgdat |> .d(target == "pcpi_pch"),
            alpha = 0.4,
            color = "gray") +
  geom_point(aes(x = pilvl,
                 y = coverage,
                 color = method),
             data = cvgdat_cpi,
             size = 3) +
  geom_line(aes(x = pilvl,
                y = coverage,
                color = method),
            data = cvgdat_cpi,
            lwd = 1.25) +
  geom_segment(aes(x = 0, y = 0, xend = 1, yend = 1),
               color = "black",
               linetype = "dashed",
               data = cvgdat_cpi) +
  #scale_color_brewer(palette = "Set1") +
  facet_grid(source ~ error_method)+

  ggtitle("Inflation") +

  scale_color_met_d("Hokusai1") +

  ylab("Empirical Coverage Level (Central PI)") +
  xlab("Nominal Coverage (Central PI)") +
  theme_uqimf()

plot_gdp <- ggplot() +
  geom_line(aes(x = pilvl,
                y = coverage,
                group = idcol),
            data = large_cvgdat |> .d(target == "ngdp_rpch"),
            alpha = 0.4,
            color = "gray") +
  geom_point(aes(x = pilvl,
                 y = coverage,
                 color = method),
             data = cvgdat_gdp,
             size = 3) +
  geom_line(aes(x = pilvl,
                y = coverage,
                color = method),
            data = cvgdat_gdp,
            lwd = 1.25) +
  geom_segment(aes(x = 0, y = 0, xend = 1, yend = 1),
               color = "black",
               linetype = "dashed",
               data = cvgdat_gdp) +
  #scale_color_brewer(palette = "Set1") +
  facet_grid(source ~ error_method)+

  ggtitle("Real GDP Growth") +

  scale_color_met_d("Hokusai1") +

  ylab("Empirical Coverage Level (Central PI)") +
  xlab("Nominal Coverage (Central PI)") +
  theme_uqimf()

```

## GDP

```{r hey3, echo = FALSE}
scores <- fread(here("quantile_forecasts", "ci_scores.csv"))

wis_scores <- fread(here("quantile_forecasts", "ci_scores_avgcnt.csv")) |>
  data.table::copy() |>
  .d(, .(model, error_method, method, target, horizon, interval_score, dispersion, underprediction, overprediction)) |>
  setnames("model", "source")

crps_scores <- fread(here("quantile_forecasts", "sample_scores.csv"))

all_scores <- 
  crps_scores[wis_scores, on = c("source", "error_method", "method", "target", "horizon")]|>
  .d(error_method == "absolute") |>
  .d(, error_method := NULL)

gather_scores <- all_scores |>
  data.table::copy() |>
  .d(target == "ngdp_rpch") |>
  .d(,target := NULL) |>
  .d(, .(horizon, method, source, score, interval_score)) |>
  setnames("score", "sample_crps") |>
  melt(id.vars = c("horizon", "method", "source"), variable.name = "score_type", value.name = "score") |>
  .d(, combms := paste0(method,"_", score_type)) |>
  .d(, .(horizon, source, combms, score)) |>
  .d(, horizon := paste0("horizon = ", horizon)) |>
  .d(, score := round(score, 3)) |>
  dcast(horizon + combms ~ source, value.var = "score")

gather_scores |>
  data.table::copy() |>
  gt(rowname_col = "combms", groupname_col = "horizon") |>
  cols_label(
      IMF = "IMF",
      ar = "ar",
      bvar = "bvar"
    )

col_names <- c("IMF", "ar", "bvar")

```

```{r, echo = FALSE, warning=FALSE,fig.dim = c(10, 12)}

plots_is <- vector(mode = "list", length = 4)
plots_cr <- vector(mode = "list", length = 4)

for(i in 1:4){

  hor <- (i-1)*0.5

  mydat <- gather_scores |>
    .d(horizon == paste0("horizon = ", hor)) |>
  .d(grep("interval", combms)) |>
  melt(id.vars = c("horizon", "combms"), variable.name = "source", value.name = "score") |>
  .d(, c("method", "scorem", "extra") := tstrsplit(combms, "_", fixed=TRUE))

  plots_is[[i]] <- ggplot(mydat, aes(x = source, y = method)) +
  geom_tile(aes(fill = score)) +
    guides(fill = FALSE) +
    ggtitle(paste0("horizon = ", hor, " - Weighted Interval Score"))
}

for(i in 1:4){

  hor <- (i-1)*0.5

  mydat <- gather_scores |>
    .d(horizon == paste0("horizon = ", hor)) |>
  .d(grep("crps", combms)) |>
  melt(id.vars = c("horizon", "combms"), variable.name = "source", value.name = "score")|>
  .d(, c("method", "scorem", "extra") := tstrsplit(combms, "_", fixed=TRUE))

  plots_cr[[i]] <- ggplot(mydat, aes(x = source, y = method)) +
  geom_tile(aes(fill = score))+
    guides(fill = FALSE)+
    ggtitle(paste0("horizon = ", hor, " - CRPS by sample"))
}

ovr_plot <- 
  (plots_is[[1]] + plots_cr[[1]]) /
  (plots_is[[2]] + plots_cr[[2]]) /
  (plots_is[[3]] + plots_cr[[3]]) /
  (plots_is[[4]] + plots_cr[[4]]) +
  plot_layout(heights = c(1, 1,1,1)) &
    plot_annotation(tag_levels = 'I')  &
    theme(legend.position = 'right', 
          legend.box="vertical", legend.margin=margin())

ovr_plot

```

```{r cvgdat, include=FALSE, echo = FALSE}

scores <- fread(here("quantile_forecasts", "ci_scores.csv"))
scores_cvgshort <- fread(here("quantile_forecasts", "cvg_pooled.csv"))

cvg_rg <- c(50, 80)

cols <- paste0("coverage_", cvg_rg)

large_cvgdat <- scores |>
  setnames("model", "source") |>
  .d(, c("country", "horizon", "target", "error_method", "method", "source", cols), with = FALSE) |>
  melt(id.vars = c("country", "horizon", "target", "error_method", "method", "source"),
       variable.name = "pilvl",
       value.name = "coverage") |>
  .d(, pilvl := gsub("^.*?coverage_","",pilvl)) |>
  .d(, pilvl := as.numeric(pilvl)/100) |>
  .d(, idcol := paste0(horizon, country, method)) |>
  .d(, country := NULL) |>
  .d(, horizon := NULL)

cvgdat <- scores_cvgshort |>
  setnames("model", "source") |>
  .d(, c( "target", "error_method", "method", "source", cols), with = FALSE) |>
  melt(id.vars = c("target", "error_method", "method", "source"),
       variable.name = "pilvl",
       value.name = "coverage") |>
  .d(, pilvl := gsub("^.*?coverage_","",pilvl)) |>
  .d(, pilvl := as.numeric(pilvl)/100)

cvgdat_cpi <- cvgdat |>
  .d(target == "pcpi_pch")

cvgdat_gdp <- cvgdat |>
  .d(target == "ngdp_rpch")

plot_cpi <- ggplot() +
  geom_line(aes(x = pilvl,
                y = coverage,
                group = idcol),
            data = large_cvgdat |> .d(target == "pcpi_pch"),
            alpha = 0.4,
            color = "gray") +
  geom_point(aes(x = pilvl,
                 y = coverage,
                 color = method),
             data = cvgdat_cpi,
             size = 3) +
  geom_line(aes(x = pilvl,
                y = coverage,
                color = method),
            data = cvgdat_cpi,
            lwd = 1.25) +
  geom_segment(aes(x = 0, y = 0, xend = 1, yend = 1),
               color = "black",
               linetype = "dashed",
               data = cvgdat_cpi) +
  #scale_color_brewer(palette = "Set1") +
  facet_grid(source ~ error_method)+

  ggtitle("Inflation") +

  scale_color_met_d("Hokusai1") +

  ylab("Empirical Coverage Level (Central PI)") +
  xlab("Nominal Coverage (Central PI)") +
  theme_uqimf()

plot_gdp <- ggplot() +
  geom_line(aes(x = pilvl,
                y = coverage,
                group = idcol),
            data = large_cvgdat |> .d(target == "ngdp_rpch"),
            alpha = 0.4,
            color = "gray") +
  geom_point(aes(x = pilvl,
                 y = coverage,
                 color = method),
             data = cvgdat_gdp,
             size = 3) +
  geom_line(aes(x = pilvl,
                y = coverage,
                color = method),
            data = cvgdat_gdp,
            lwd = 1.25) +
  geom_segment(aes(x = 0, y = 0, xend = 1, yend = 1),
               color = "black",
               linetype = "dashed",
               data = cvgdat_gdp) +
  #scale_color_brewer(palette = "Set1") +
  facet_grid(source ~ error_method)+

  ggtitle("Real GDP Growth") +

  scale_color_met_d("Hokusai1") +

  ylab("Empirical Coverage Level (Central PI)") +
  xlab("Nominal Coverage (Central PI)") +
  theme_uqimf()

```

# Coverage, by target, methods and source

```{r cvgplot, fig.dim = c(10, 12), echo = FALSE}

ovr_plot <- 
  (plot_gdp) /
  (plot_cpi) +
  plot_layout(guides = "collect", 
              heights = c(1, 1)) &
    plot_annotation(tag_levels = 'I')  &
    theme(legend.position = 'bottom', 
          legend.box="vertical", legend.margin=margin())

ovr_plot

```

```{r loaddata, include = FALSE, echo = FALSE}

sub_weodat <- 
   data.table::fread(here("WEOforecasts_tidy.csv")) |>
      .d(g7 == 1,) |>
      .d(horizon < 2) |> ######################this shall be extended sometime##############
      .d(, error := prediction - tv_1) |>
      .d(target_year < 2015) |>
      .d(, .(country, prediction, target, error,
             horizon, target_year, forecast_year,
             tv_1)
      )

```

```{r, include = FALSE, echo = FALSE}
head(sub_weodat)
```

### 2023-09-06 manuscript/manuscript.tex
visualize scores and coverage

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
]{article}
\usepackage{amsmath,amssymb}
\usepackage{lmodern}
\usepackage{setspace}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\usepackage[margin=1in]{geometry}
\usepackage{color}
\usepackage{fancyvrb}
\newcommand{\VerbBar}{|}
\newcommand{\VERB}{\Verb[commandchars=\\\{\}]}
\DefineVerbatimEnvironment{Highlighting}{Verbatim}{commandchars=\\\{\}}
% Add ',fontsize=\small' for more characters per line
\usepackage{framed}
\definecolor{shadecolor}{RGB}{248,248,248}
\newenvironment{Shaded}{\begin{snugshade}}{\end{snugshade}}
\newcommand{\AlertTok}[1]{\textcolor[rgb]{0.94,0.16,0.16}{#1}}
\newcommand{\AnnotationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\AttributeTok}[1]{\textcolor[rgb]{0.77,0.63,0.00}{#1}}
\newcommand{\BaseNTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
\newcommand{\BuiltInTok}[1]{#1}
\newcommand{\CharTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
\newcommand{\CommentTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textit{#1}}}
\newcommand{\CommentVarTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\ConstantTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
\newcommand{\ControlFlowTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{\textbf{#1}}}
\newcommand{\DataTypeTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{#1}}
\newcommand{\DecValTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
\newcommand{\DocumentationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\ErrorTok}[1]{\textcolor[rgb]{0.64,0.00,0.00}{\textbf{#1}}}
\newcommand{\ExtensionTok}[1]{#1}
\newcommand{\FloatTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
\newcommand{\FunctionTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
\newcommand{\ImportTok}[1]{#1}
\newcommand{\InformationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\KeywordTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{\textbf{#1}}}
\newcommand{\NormalTok}[1]{#1}
\newcommand{\OperatorTok}[1]{\textcolor[rgb]{0.81,0.36,0.00}{\textbf{#1}}}
\newcommand{\OtherTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{#1}}
\newcommand{\PreprocessorTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textit{#1}}}
\newcommand{\RegionMarkerTok}[1]{#1}
\newcommand{\SpecialCharTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
\newcommand{\SpecialStringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
\newcommand{\StringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
\newcommand{\VariableTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
\newcommand{\VerbatimStringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
\newcommand{\WarningTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\usepackage{longtable,booktabs,array}
\usepackage{calc} % for calculating minipage widths
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{5}
\usepackage{lineno}
\linenumbers
\newcommand{\beginsupplement}{\setcounter{table}{0}  \renewcommand{\thetable}{S\arabic{table}} \setcounter{figure}{0} \renewcommand{\thefigure}{S\arabic{figure}}}
\usepackage{float}
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  pdftitle={Compare forecats},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}

\title{Compare forecats}
\author{}
\date{\vspace{-2.5em}}

@@

\setstretch{2}
\hypertarget{r-markdown}{%
\subsection{R Markdown}\label{r-markdown}}

This is an R Markdown document. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see \url{http://rmarkdown.rstudio.com}.

When you click the \textbf{Knit} button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document. You can embed an R code chunk like this:

\begin{Shaded}
\begin{Highlighting}[]
\FunctionTok{summary}\NormalTok{(cars)}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
##      speed           dist       
##  Min.   : 4.0   Min.   :  2.00  
##  1st Qu.:12.0   1st Qu.: 26.00  
##  Median :15.0   Median : 36.00  
##  Mean   :15.4   Mean   : 42.98  
##  3rd Qu.:19.0   3rd Qu.: 56.00  
##  Max.   :25.0   Max.   :120.00
\end{verbatim}

\hypertarget{including-plots}{%
\subsection{Including Plots}\label{including-plots}}

You can also embed plots, for example:

\includegraphics{manuscript_files/figure-latex/pressure-1.pdf}

Note that the \texttt{echo\ =\ FALSE} parameter was added to the code chunk to prevent printing of the R code that generated the plot.

>>>>

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
]{article}
\usepackage{amsmath,amssymb}
\usepackage{lmodern}
\usepackage{setspace}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\usepackage[margin=1in]{geometry}
\usepackage{longtable,booktabs,array}
\usepackage{calc} % for calculating minipage widths
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{5}
\usepackage{lineno}
\linenumbers
\newcommand{\beginsupplement}{\setcounter{table}{0}  \renewcommand{\thetable}{S\arabic{table}} \setcounter{figure}{0} \renewcommand{\thefigure}{S\arabic{figure}}}
\usepackage{float}
\usepackage{booktabs}
\usepackage{caption}
\usepackage{longtable}
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  pdftitle={IMF and Benchmark Forecasts},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}

\title{IMF and Benchmark Forecasts}
\author{}
\date{\vspace{-2.5em}}

@@

\setstretch{2}
\hypertarget{a-short-note-on-error-handling}{%
\section{A short note on error handling}\label{a-short-note-on-error-handling}}

In almost all 72 cases, absolute error handling gives lower scores than directional error handling. The only exception is the inflation series for the IMF forecasts and horizon 0, where the expanding window and rolling window method give \textit{slightly} lower scores for the directional methodology.
We thus decide to focus on the absolute errors in this document.

\hypertarget{scores-by-estimation-method-horizon-and-forecast-source}{%
\section{Scores, by estimation method, Horizon and forecast source}\label{scores-by-estimation-method-horizon-and-forecast-source}}

\begin{longtable}{l|rrr}
\toprule
\multicolumn{1}{l}{} & IMF & ar & bvar \\ 
\midrule
\multicolumn{4}{l}{horizon = 0} \\ 
\midrule
expanding window\_interval\_score & 0.115 & 0.123 & 0.122 \\ 
expanding window\_sample\_crps & 0.087 & 0.092 & 0.091 \\ 
leave-one-out\_interval\_score & 0.119 & 0.133 & 0.134 \\ 
leave-one-out\_sample\_crps & 0.088 & 0.099 & 0.100 \\ 
rolling window\_interval\_score & 0.119 & 0.128 & 0.126 \\ 
rolling window\_sample\_crps & 0.094 & 0.097 & 0.098 \\ 
\midrule
\multicolumn{4}{l}{horizon = 0.5} \\ 
\midrule
expanding window\_interval\_score & 0.258 & 0.272 & 0.296 \\ 
expanding window\_sample\_crps & 0.182 & 0.208 & 0.241 \\ 
leave-one-out\_interval\_score & 0.261 & 0.313 & 0.317 \\ 
leave-one-out\_sample\_crps & 0.180 & 0.217 & 0.230 \\ 
rolling window\_interval\_score & 0.261 & 0.266 & 0.288 \\ 
rolling window\_sample\_crps & 0.191 & 0.201 & 0.235 \\ 
\midrule
\multicolumn{4}{l}{horizon = 1} \\ 
\midrule
expanding window\_interval\_score & 0.448 & 0.737 & 0.590 \\ 
expanding window\_sample\_crps & 0.327 & 0.504 & 0.426 \\ 
leave-one-out\_interval\_score & 0.427 & 0.726 & 0.600 \\ 
leave-one-out\_sample\_crps & 0.302 & 0.448 & 0.400 \\ 
rolling window\_interval\_score & 0.451 & 0.739 & 0.591 \\ 
rolling window\_sample\_crps & 0.333 & 0.514 & 0.434 \\ 
\midrule
\multicolumn{4}{l}{horizon = 1.5} \\ 
\midrule
expanding window\_interval\_score & 0.495 & 1.044 & 0.800 \\ 
expanding window\_sample\_crps & 0.346 & 0.627 & 0.602 \\ 
leave-one-out\_interval\_score & 0.487 & 1.103 & 0.903 \\ 
leave-one-out\_sample\_crps & 0.337 & 0.583 & 0.577 \\ 
rolling window\_interval\_score & 0.494 & 1.041 & 0.779 \\ 
rolling window\_sample\_crps & 0.347 & 0.632 & 0.570 \\ 
\bottomrule
\end{longtable}

\hypertarget{inflation}{%
\subsection{Inflation}\label{inflation}}

\includegraphics{manuscript_files/figure-latex/unnamed-chunk-2-1.pdf}

\hypertarget{gdp}{%
\subsection{GDP}\label{gdp}}

\begin{longtable}{l|rrr}
\toprule
\multicolumn{1}{l}{} & IMF & ar & bvar \\ 
\midrule
\multicolumn{4}{l}{horizon = 0} \\ 
\midrule
expanding window\_interval\_score & 0.241 & 0.301 & 0.298 \\ 
expanding window\_sample\_crps & 0.178 & 0.209 & 0.204 \\ 
leave-one-out\_interval\_score & 0.257 & 0.312 & 0.310 \\ 
leave-one-out\_sample\_crps & 0.183 & 0.219 & 0.214 \\ 
rolling window\_interval\_score & 0.240 & 0.302 & 0.297 \\ 
rolling window\_sample\_crps & 0.178 & 0.211 & 0.204 \\ 
\midrule
\multicolumn{4}{l}{horizon = 0.5} \\ 
\midrule
expanding window\_interval\_score & 0.416 & 0.540 & 0.493 \\ 
expanding window\_sample\_crps & 0.298 & 0.383 & 0.358 \\ 
leave-one-out\_interval\_score & 0.448 & 0.583 & 0.531 \\ 
leave-one-out\_sample\_crps & 0.310 & 0.408 & 0.377 \\ 
rolling window\_interval\_score & 0.416 & 0.554 & 0.504 \\ 
rolling window\_sample\_crps & 0.297 & 0.405 & 0.373 \\ 
\midrule
\multicolumn{4}{l}{horizon = 1} \\ 
\midrule
expanding window\_interval\_score & 0.837 & 1.090 & 0.942 \\ 
expanding window\_sample\_crps & 0.640 & 0.822 & 0.763 \\ 
leave-one-out\_interval\_score & 0.858 & 1.067 & 0.948 \\ 
leave-one-out\_sample\_crps & 0.634 & 0.759 & 0.709 \\ 
rolling window\_interval\_score & 0.851 & 1.122 & 0.970 \\ 
rolling window\_sample\_crps & 0.663 & 0.875 & 0.815 \\ 
\midrule
\multicolumn{4}{l}{horizon = 1.5} \\ 
\midrule
expanding window\_interval\_score & 1.045 & 1.288 & 1.102 \\ 
expanding window\_sample\_crps & 0.790 & 0.937 & 0.897 \\ 
leave-one-out\_interval\_score & 1.034 & 1.278 & 1.107 \\ 
leave-one-out\_sample\_crps & 0.765 & 0.882 & 0.849 \\ 
rolling window\_interval\_score & 1.056 & 1.312 & 1.143 \\ 
rolling window\_sample\_crps & 0.831 & 0.985 & 0.949 \\ 
\bottomrule
\end{longtable}

\includegraphics{manuscript_files/figure-latex/unnamed-chunk-3-1.pdf}

\hypertarget{coverage-by-target-methods-and-source}{%
\section{Coverage, by target, methods and source}\label{coverage-by-target-methods-and-source}}

\includegraphics{manuscript_files/figure-latex/cvgplot-1.pdf}
